A python toolbox to tackle the curse of imbalanced datasets in machine learning

### 2016-06-26 main.tex
add pipeline

The implementation rely on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn}.
Each class implements 3 main functions inspired from the \texttt{scikit-learn} API:
(i) \texttt{fit} computes the parameter values which are later needed to transform the data into a balanced set;
(ii) \texttt{sample} performs the sampling and return the data with the desired balancing ratio;
and (iii) \texttt{fit\_sample} is equivalent of calling the function \texttt{fit} followed by the function \texttt{transform}.

>>>>

The implementation rely on \texttt{numpy}, \texttt{scipy}, and \texttt{scikit-learn}.
Each class implements 3 main functions inspired from the \texttt{scikit-learn} API:
(i) \texttt{fit} computes the parameter values which are later needed to transform the data into a balanced set;
(ii) \texttt{sample} performs the sampling and return the data with the desired balancing ratio;
and (iii) \texttt{fit\_sample} is equivalent of calling the function \texttt{fit} followed by the function \texttt{sample}.
A class \texttt{Pipeline} is inherited from \texttt{scikit-learn} toolbox to automatically combine \texttt{sampler}, \texttt{transformers}, and \texttt{estimators}.
